	\years{2013}Seo, Sang-Hyup, Seo, Jong-Hyun, and Kim, Hyun-Min, ``Newton’s Method for Solving a Quadratic Matrix Equation with Special Coefficient Matrices'', {\it Honam Math. J.}, 35(3), 417--433, Sep. 2013. \\
	\years{2018}Meng, J., Seo, S. \& Kim, H. ``Condition Numbers and Backward Error of a Matrix Polynomial Equation Arising in Stochastic Models'', {\it J. Sci. Comput.} 76, 759--776 (2018). \\
	\years{2018}Seo, Sang-Hyup, Seo, Jong-Hyeon, and Kim, Hyun-Min, ``A Modified Newton Method for a Matrix Polynomial Equation Arising in Stochastic Problem'', {\it Electron. J. Linear Algebra}, 34, 500--513, 2018. \\
	\years{2019}Kim, Taehyeong, Sang-Hyup Seo, and Hyun-Min Kim. ``On Newton's Method for Solving a System of Nonlinear Matrix Equations.'' {\it East Asian Math. J.} 35(3), 341--349, 2019. \\
	\years{2020}Seo, Sang-hyup, and Jong-Hyeon Seo. ``Convergence of relaxed Newton method for order-convex matrix equations'', {\it Comput. Appl. Math.} 39(1), 1--17, 2020. \\
	\years{2023}Na Hyeon Lee, Seon Hee Kim, Sang-Hyup Seo, Byeong-Jun Kim, Chi-Seung Lee, Gil Hwan Kim, Sung Jin Park, Seon Hyun Kim, Dong Yeon Ryu, Ho Hyun Kim, Sang Bong Lee, Chan Ik Park, and Jae Hun Kim, ``Prediction of respiratory complications by quantifying lung contusion volume using chest computed tomography in patients with chest trauma'', {\it Sci Rep.} 13(1):6387, Apr 2023. \\
	\years{2023}Giphil Cho, Young Jin Kim, Sang-hyup Seo, Geunsoo Jang, and Hyojung Lee, ``Cost-effectiveness analysis of COVID-19 variants effects in an age-structured model'', {\it Sci Rep.} 13: 15844, 2023.