% Compact Academic CV
% LaTeX Template
% Version 2.0 (6/7/2019)
%
% This template originates from:
% https://www.LaTeXTemplates.com
%
% Authors:
% Dario Taraborelli (http://nitens.org/taraborelli/home)
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{article} % Default document font size
\usepackage{kotex}
\usepackage{enumitem}
\usepackage{longtable}
\usepackage{etoolbox}
\usepackage{fontawesome5}

\input{structure.tex} 

%----------------------------------------------------------------------------------------
%	CONFIGURATION
%----------------------------------------------------------------------------------------

\renewcommand{\baselinestretch}{1.3}

%================
% MACRO DEFINITIONS (etoolbox \appto 사용으로 안전성 확보)
%================

% 1. CAREER
\newcommand\mycareer{}
\newcommand\mycareereng{}
\newcommand\myedu{}
\newcommand\myedueng{}

\newcommand\addcareer[6]{
    \appto\mycareer{
        \noindent % 들여쓰기 방지
        {\large\bfseries #1} \hfill {\color{gray}\small #3 -- #4} \\ % 회사명 --- 기간
        {\color{RoyalBlue}\textbf{#5}} \par % 직함 (파란색 강조)
        \vspace{0.8em} % 항목 간 간격 추가
    }
    \appto\mycareereng{
        \noindent
        {\large\bfseries #2} \hfill {\color{gray}\small #3 -- #4} \\ 
        {\color{RoyalBlue}\textbf{#6}} \par 
        \vspace{0.8em}
    }
}

\newcommand\addedu[5]{
	\appto\myedu{
		{\large\bfseries #1} \hfill {\color{gray}\small #4 -- #5} \\
        {\color[HTML]{111199} \faGraduationCap \ \textbf{#3}} \par
        \vspace{0.8em}
	}

	\appto\myedueng{
		{\large\bfseries #2} \hfill {\color{gray}\small #4 -- #5} \\
        {\color[HTML]{111199} \faGraduationCap \ \textbf{#3}} \par
        \vspace{0.8em}
	}
}

% 2. PROJECT
\newcommand\myprojs{}
\newcommand\myprojseng{}

\newcommand\addproject[9]{
    \appto\myprojs{
        \begin{tabular}{cl}
			\multicolumn{2}{p{\linewidth}}{\textbf{#1}} \\
			\faUserTag & {\color{darkgray}#3} \\
			\faWonSign & {\color{darkgray}#5} \\
			\faCalendar*[regular] & {\color{darkgray}#7} \\
			\faBuilding[regular] & {\color{darkgray}#8}
		\end{tabular}
		\medskip\par
    }
    \appto\myprojseng{
        \begin{tabular}{cl}
			\multicolumn{2}{p{\linewidth}}{\textbf{#2}} \\
			\faUserTag & {\color{darkgray}#4} \\
			\faDollarSign & {\color{darkgray}#6} \\
			\faCalendar*[regular] & {\color{darkgray}#7} \\
			\faBuilding[regular] & {\color{darkgray}#9}
		\end{tabular}
		\medskip\par
    }
}

% 3. PAPER
\newcommand{\mypapers}{}

% [중요] \years 명령어가 안전하게 들어가도록 수정
\newcommand{\addpaper}[5]{
    \appto\mypapers{
        \years{#1}#2, ``#3'', {\it #4}, #5.\par
    }
}

%----------------------------------------------------------------------------------------
%	PROFILE
%----------------------------------------------------------------------------------------
\newcommand\profile{
	{\Huge\bfseries 서상협 (Seo, Sang-hyup)} \par \vspace{1em}
	
	% 아이콘을 활용하여 정보 밀도를 높임
	{\Large
		\begin{tabular}{cp{\dimexpr\linewidth-2.5em}}
			\faMapMarker*\ & 부산광역시 부산진구 자유평화로37번길 67 2603호 \\ 
			\faMobile*\ & 010-4545-9199 \\
			\faEnvelope\ & \href{mailto:saibie1677@gmail.com}{saibie1677@gmail.com}
		\end{tabular}
	}
	\vspace{1em} % 프로필과 본문 사이 간격
}

\newcommand\profileeng{
	{\Huge\bfseries Seo, Sang-hyup} \par \vspace{1em}
	
	{\large
		\begin{tabular}{cp{\dimexpr\linewidth-2.5em}}
			\faMapMarker*\ & 47362, No.2603, 67, Jayupyeonghwa-ro 37beon-gil, Busanjin-gu, Busan, Rep. of Korea \\
			\faMobile*\ & +82-10-4545-9199 \\
			\faEnvelope\ & \href{mailto:saibie1677@gmail.com}{saibie1677@gmail.com}
		\end{tabular}
	}
	\vspace{1em}
}

% \newcommand\profile{
% 	{\LARGE\bfseries 서상협 (Seo, Sang-hyup)} 
% 	\bigskip\bigskip\medskip 
	
% 	부산광역시 부산진구 자유평화로37번길 67 2603호 
% 	\medskip 
	
% 	휴대전화 : 010-4545-9199 
% 	\medskip 
	
% 	E-mail: \href{mailto:saibie1677@gmail.com}{saibie1677@gmail.com}\\ 
% }

% \newcommand\profileeng{
% 	{\LARGE\bfseries Seo, Sang-hyup (서상협)} 
% 	\bigskip\bigskip\medskip 
	
% 	47362, No.2603, 67, Jayupyeonghwa-ro 37beon-gil, Busanjin-gu, Busan, Republic of Korea 
% 	\medskip 
	
% 	Mobile : +82-10-4545-9199 
% 	\medskip 
	
% 	E-mail: \href{mailto:saibie1677@gmail.com}{saibie1677@gmail.com}\\ 
% }

%================
% EDUCATION
%================
\addedu{이학박사, 부산대학교}
{Ph.D., Pusan National University}
{Accelerations of Newton's Methods Solving Nonlinear Matrix Equations}
{2012.03}{2019.02}

\addedu{이학석사, 부산대학교}
{M.S., Pusan National University}
{The Numerical Method for Solving a Quadratic Matrix Equation with Special Coefficient Matrices}
{2010.03}{2012.02}


%================
% DATA ENTRY
%================

% CAREER
\addcareer{(주)스마트소셜}{Smart Social, Inc.}{2023.02}{\phantom{0000.00}}{선임연구원 / 팀장}{Senior Researcher / Team Lead}
\addcareer{국가수리과학연구소}{National Institute for Mathematical Sciences}{2019.10}{2022.09}{박사후연구원}{Postdoctoral Researcher}
\addcareer{부산대학교}{Pusan National University}{2019.03}{2019.09}{박사후연구원}{Postdoctoral Researcher} 
\addcareer{(주)스마트소셜}{Smart Social, Inc.}{2017.03}{2017.10}{사원 : 데이터베이스 분석, 상품 및 과제 기획}{Associate : DB Analysis, Product \& Project Planning}

% PAPER
\addpaper{2013}
{\textbf{Seo, Sang-Hyup}, Seo, Jong-Hyun, and Kim, Hyun-Min}
{Newton’s Method for Solving a Quadratic Matrix Equation with Special Coefficient Matrices}
{Honam Math. J.}
{35(3), 417--433, Sep. 2013}

\addpaper{2018}
{Meng, J., \textbf{Seo, S.} \& Kim, H.}
{Condition Numbers and Backward Error of a Matrix Polynomial Equation Arising in Stochastic Models}
{J. Sci. Comput.}
{76, 759--776 (2018)}

\addpaper{2018}
{\textbf{Seo, Sang-Hyup}, Seo, Jong-Hyeon, and Kim, Hyun-Min}
{A Modified Newton Method for a Matrix Polynomial Equation Arising in Stochastic Problem}
{Electron. J. Linear Algebra}
{34, 500--513, 2018}

\addpaper{2019}
{Kim, Taehyeong, \textbf{Sang-Hyup Seo}, and Hyun-Min Kim}
{On Newton's Method for Solving a System of Nonlinear Matrix Equations}
{East Asian Math. J.}
{35(3), 341--349, 2019}

\addpaper{2020}
{\textbf{Seo, Sang-hyup}, and Jong-Hyeon Seo}
{Convergence of relaxed Newton method for order-convex matrix equations}
{Comput. Appl. Math.}
{39(1), 1--17, 2020}

\addpaper{2023}
{Na Hyeon Lee, Seon Hee Kim, \textbf{Sang-Hyup Seo}, Byeong-Jun Kim, Chi-Seung Lee, Gil Hwan Kim, Sung Jin Park, Seon Hyun Kim, Dong Yeon Ryu, Ho Hyun Kim, Sang Bong Lee, Chan Ik Park, and Jae Hun Kim}
{Prediction of respiratory complications by quantifying lung contusion volume using chest computed tomography in patients with chest trauma}
{Sci Rep.}
{13(1):6387, Apr 2023}

\addpaper{2023}
{Giphil Cho, Young Jin Kim, \textbf{Sang-hyup Seo}, Geunsoo Jang, and Hyojung Lee}
{Cost-effectiveness analysis of COVID-19 variants effects in an age-structured model}
{Sci Rep.}
{13: 15844, 2023}

% PROJECT
\addproject
{산업수학 문제해결 연구}
{Research on solving problems of industrial mathematics}
{참여연구원}{Co-investigator}
{5,947,000,000}{5,947,000}
{2019.10 -- 2022.09}
{국가수리과학연구소}{National Institute for Mathematical Sciences}

\addproject
{안과질환 진단서비스 플랫폼 개발사업}
{Development of a Service Platform for Ophthalmology Disease Diagnosis}
{참여연구원}{Co-investigator}
{98,000,000}{98,000}
{2019.05 -- 2020.12}
{부산광역시}{Busan Metropolitan City}

\addproject
{부산광역시 의료수학 생태계 조성사업}
{Ecosystem grant for medical and industrial mathematics in Busan}
{참여연구원}{Co-investigator}
{320,000,000}{320,000}
{2020.01 -- 2022.09}
{부산광역시}{Busan Economic Promotion Agency}

\addproject
{아프리카 돼지열병 발생시 효과적인 차단 방역지대 설정 연구}
{Study on establishing effective blocking zones for the spread of Africa swine fever}
{참여연구원}{Co-investigator}
{225,000,000}{225,000}
{2020.04 -- 2021.12}
{농림축산식품부}{Ministry of Agriculture, Food and Rural Affairs}

\addproject
{데이터 기반 감염병 유행 예측 수리모델 개발과 완화전략 분석}
{Development of mathematical model for data-based infectious disease outbreak prediction and mitigation strategy analysis}
{참여연구원}{Co-investigator}
{201,398,000}{201,398}
{2021.09 -- 2022.09}
{한국연구재단}{National Research Foundation of Korea}

\addproject
{탄소중립 대응 친환경 섬유소재 개발 디지털 전환 인공지능 플랫폼 구축}
{AI platform establishment of eco-friendly textile material development digital conversion for Carbon-neutral}
{참여연구원}{Co-investigator}
{100,000,000}{100,000}
{2022.07 -- 2022.09}
{한국산업기술진흥원}{Korea Institute for Advancement of Technology}


%================
% PRESENT
%================
\newcommand\mypresent{
	\begin{itemize}[leftmargin=*]
		\item ``Ophthalmic Disease Diagnosis Based on Convolutional Neural Network'', {\it KSIAM 2020 Annual Meeting}, KAL Hotel in Jeju, Korea, Nov. 12--15, 2020.
		\item ``Convergence of a Modified Newton Method for a Matrix Polynomial Equation Arising in Stochastic Problems'', {\it Numerical Analysis and Scientific Computation with Applications 2018}, Elite City Resort in Kalamata, Greece, Jul. 2--6, 2018.
		\item ``Convergence of Newton Iterations for Order-Convex Matrix Functions'', {\it SIAM Conference on Applied Linear Algebra}, Hyatt Regency Atlanta, USA, Oct. 26-30, 2015.
		\item ``The Existence and Convergence of Two Iterations for Differentiable Order-Convex Matrix Functions'', {\it The 2014 International Conference on Tensors and Matrices and their Applications}, Suzhou, China, Dec. 16--19, 2014.
		\item ``The Newton and the Fixed Point Iterations for Differentiable Order-Convex Matrix Functions'', {\it International Linear Algebra Society Conference 2014}, Sungkyunkwan University, Korea, Aug. 6--9, 2014.
		\item ``The Monotone Convergence of Newton’s Method for Differentiable Convex Matrix Functions'', {\it Hakata Workshop 2014}, Kyushu, Japan, Feb. 8, 2014.
		\item ``The Elementwise Convex Condition for Differentiable Matrix Functions'', {\it AKOOS-PNU}, Pusan National University, Korea, Feb. 5--7, 2014.
		\item ``Newton’s method for solving a quadratic matrix equation with special coefficient matrices'', {\it KOOK-TAPU Joint Seminar 2013}, Osaka City University, Japan, Jul. 22--26, 2013.
	\end{itemize}
}

%================
% POSTER
%================
\newcommand\myposter{
	\begin{itemize}[leftmargin=*]
		\item ``Properties of Nonnegative, Irreducible, and $M$-Matrices'', {\it The Asian Mathematical Conference 2013}, BEXCO, Korea, Jun. 30--Jul. 4, 2013.
	\end{itemize}
}

%================
% DOCUMENT MODE
% 0 : Korean and English
% 1 : Korean
% 2 : English
%================
\ifdefined\KoreanMode
\else
\def\KoreanMode{0}
\fi


%================
% DOCUMENT START
%================
\begin{document}

%------------------------------------------------
% KOREAN SECTION
%------------------------------------------------
\if\KoreanMode2
\else
\profile

\section*{학력}
\myedu

\section*{경력사항}
\mycareer

\newpage
\section*{연구실적}

\subsection*{논문}
\mypapers

\newpage
\subsection*{과제참여}
\myprojs

\subsection*{발표실적}
\renewcommand\labelitemi{\tiny$\bullet$}
\mypresent

\subsection*{포스터 발표}
\myposter

\fi

%------------------------------------------------
% ENGLISH SECTION
%------------------------------------------------
\if\KoreanMode1
\else
\newpage\setcounter{page}{1}

\profileeng

\section*{Education}
\myedueng

\section*{Career}
\mycareereng

\newpage
\section*{Publications}

\subsection*{Papers}
\mypapers

\newpage
\subsection*{Projects}
\myprojseng

\subsection*{Presentations}
\renewcommand\labelitemi{\tiny$\bullet$}
\mypresent

\subsection*{Poster Presentations}
\myposter

\fi

\end{document}